An Extendable \proglang{Python} Implementation of Robust Optimisation Monte Carlo

### 2023-09-05 article/article.tex
after revision 3

# Initialize the ROMC inference method
bounds = [(-2.5, 2.5)] # bounds of the prior
parallelize = True # activate parallel execution
romc = elfi.ROMC(d, bounds = bounds, parallelize = parallelize)
\end{Code}

@@

romc.visualize_region(i = 1) # for inspecting visually the bounding box

@@

# Summarize the samples (built-in ELFI tool)
romc.result.summary()
# Number of samples  : 19300
# Sample means: theta: -0.0116

@@

# eval unnorm posterior
romc.eval_unnorm_posterior(theta = 0)

# check eval posterior
romc.eval_posterior(theta = 0)
\end{Code}

@@

\begin{table}
\begin{center}
\begin{tabular}{ c|c|c|c|c }
\hline
& \(\mu_{\theta_1}\) & \(\sigma_{\theta_1}\) & \(\mu_{\theta_2}\) & \(\sigma_{\theta_2}\) \\
\hline \hline
Rejection ABC & 0.516 & 0.142 & 0.07 & 0.172 \\
\hline
ROMC (gradient-based) & 0.501 & 0.142 & 0.033 & 0.169 \\
\hline
ROMC (Bayesian optimization) & 0.494 & 0.16 & 0.086 & 0.167 \\
\hline
ROMC (Neural Network) & 0.491 & 0.138 & 0.04 & 0.172 \\
\hline
\end{tabular}
\end{center}
\caption{Comparison of the samples obtained from the estimated
  posterior with (a) Rejection sampling and (b) the different versions
  of ROMC. We observe that the obtained samples share similar
  statistics along all methods. \label{tab:ma2}}
\end{table}

>>>>

# Initialize the ROMC inference method
bounds = [(-2.5, 2.5)] # bounds of the prior
parallelize = False # True activates parallel execution
romc = elfi.ROMC(d, bounds = bounds, parallelize = parallelize)
\end{Code}

@@

romc.visualize_region(i = 2) # for inspecting visually the bounding box

@@

# Summarize the samples (built-in ELFI tool)
romc.result.summary()
# Method: ROMC
# Number of samples: 19300
# Parameter                Mean               2.5%              97.5%
# theta:                 -0.012             -1.985              1.987

@@

# eval unnorm posterior
print("%.3f" % romc.eval_unnorm_posterior(theta = np.array([[0]])))
# 58.800

# check eval posterior
print("%.3f" % romc.eval_posterior(theta = np.array([[0]])))
# 0.289
\end{Code}

@@

\begin{table}
\begin{center}
\begin{tabular}{ c|c|c|c|c }
\hline
& \(\mu_{\theta_1}\) & \(\sigma_{\theta_1}\) & \(\mu_{\theta_2}\) & \(\sigma_{\theta_2}\) \\
\hline \hline
Rejection ABC & 0.516 & 0.142 & 0.070 & 0.172 \\
\hline
ROMC (gradient-based) & 0.501 & 0.142 & 0.033 & 0.169 \\
\hline
ROMC (Bayesian optimization) & 0.513 & 0.169 & 0.090 & 0.174 \\
\hline
ROMC (Neural Network) & 0.491 & 0.138 & 0.040 & 0.172 \\
\hline
\end{tabular}
\end{center}
\caption{Comparison of the samples obtained from the estimated
  posterior with (a) Rejection sampling and (b) the different versions
  of ROMC. We observe that the obtained samples share similar
  statistics along all methods. \label{tab:ma2}}
\end{table}
